Evaluating Perceptual Judgements on 3D Printed Bar Charts

### 2024-04-16 jds.rmd
Final revisions

One interesting facet of @clevelandGraphical1984 is the participant recruitment methodology: "For each experiment the subjects fell into two categories: (1) a group of females, mostly housewives, without substantial technical experience; (2) a mixture of males and females with substantial technical training and working in technical jobs. 
Most of the subjects in the position-length experiment participated in the position-angle experiment; in all cases repeat subjects judged the position-angle graphs first." 
It seems likely that the authors recruited individuals within their respective departments as well as their wives.
In order to replicate this atypical participant recruitment method in the modern era, members of the UNL Statistics department and their spouses, partners, and roommates were asked to participate in our study. 
This replicates the spirit of the recruitment method without the implicit assumptions that graduate students and professors are male, heterosexual, and have unemployed spouses.
A total of `r length(unique(res_all$subject))` participants completed our study; demographics are shown in \Cref{fig:demographics}.

@@

A Shiny applet was used for data collection, along with the provided kit of 3D printed charts.
Participants provided informed consent through the applet, and then were asked for demographic information (age, gender, education level). 
Then, participants were shown a "practice" page which allowed them to experiment with the data collection interface and practice estimating the ratio between the bars, as shown in \Cref{fig:practice}. This practice interface did not provide any feedback as to participant correctness, but was merely intended to familiarize the participants with the questions which would be asked as well as the process of estimating the ratio between the two bars.

@@

```{r, include = F}
res_sub_count <- res_all %>% 
  group_by(subject) %>% 
  count()
```

The participants provided a total of `r nrow(res_all)` responses.
While each participant was provided with 15 trials, `r sum(res_sub_count$n < 15)` participants did not complete the entire experiment.
All responses that incorrectly identified the smaller bar ($n = `r nrow(res_all) - nrow(res)`$) were removed from the study before analysis; this serves as a basic attention check and leaves `r nrow(res)` valid responses. 
In addition, one response was removed because the participant did not enter a valid ID for a 3D printed chart.

>>>>

One interesting facet of @clevelandGraphical1984 is the participant recruitment methodology: "For each experiment the subjects fell into two categories: (1) a group of females, mostly housewives, without substantial technical experience; (2) a mixture of males and females with substantial technical training and working in technical jobs. 
Most of the subjects in the position-length experiment participated in the position-angle experiment; in all cases repeat subjects judged the position-angle graphs first." 
It seems likely that the authors recruited individuals within their respective departments as well as their wives.
In order to replicate this atypical participant recruitment method in the modern era, members of the UNL Statistics department and their spouses, partners, and roommates were asked to participate in our study. 
This replicates the spirit of the recruitment method without the implicit assumptions that graduate students and professors are male, heterosexual, and have unemployed spouses.
A total of `r nrow(valid.users)` participants completed our study; demographics are shown in \Cref{fig:demographics}.

@@

A Shiny applet was used for data collection, along with the provided kit of 3D printed charts.
Participants provided informed consent through the applet, and then were asked for demographic information (age, gender, education level). 
Then, participants were shown a "practice" page which allowed them to experiment with the data collection interface and practice estimating the ratio between the bars, as shown in \Cref{fig:practice}. This practice interface did not provide any numeric feedback as to participant correctness, but was merely intended to familiarize the participants with the questions which would be asked as well as the process of estimating the ratio between the two bars.

@@

```{r, include = F}
res_sub_count <- res_all %>% 
  group_by(nickname, participantUnique, appStartTime, subject) %>% 
  count()
```

The participants provided a total of `r nrow(res_all)` responses.
While each participant was provided with 15 trials, `r sum(res_sub_count$n < 15)` participants partially completed the experiment; one participant did not advance beyond the demographic page. 
All responses that incorrectly identified the smaller bar ($n = `r nrow(res_all) - nrow(res)`$) were removed from the study before analysis; this serves as a basic attention check and leaves `r nrow(res)` valid responses. 
In addition, one response was removed because the participant did not enter a valid ID for a 3D printed chart.

### 2024-04-16 jds.tex
Final revisions

One interesting facet of \citet{clevelandGraphical1984} is the participant recruitment methodology: ``For each experiment the subjects fell into two categories: (1) a group of females, mostly housewives, without substantial technical experience; (2) a mixture of males and females with substantial technical training and working in technical jobs.
Most of the subjects in the position-length experiment participated in the position-angle experiment; in all cases repeat subjects judged the position-angle graphs first.''
It seems likely that the authors recruited individuals within their respective departments as well as their wives.
In order to replicate this atypical participant recruitment method in the modern era, members of the UNL Statistics department and their spouses, partners, and roommates were asked to participate in our study.
This replicates the spirit of the recruitment method without the implicit assumptions that graduate students and professors are male, heterosexual, and have unemployed spouses.

A total of 38 participants completed the study; demographics are shown in \Cref{fig:demographics}.
The participants provided a total of \texttt{nrow(res\_all)} responses.

@@

A Shiny applet was used for data collection, along with the provided kit of 3D printed charts.
Participants provided informed consent through the applet, and then were asked for demographic information (age, gender, education level).
Then, participants were shown a ``practice'' page which allowed them to experiment with the data collection interface and practice estimating the ratio between the bars, as shown in \Cref{fig:practice}. This practice interface did not provide any feedback as to participant correctness, but was merely intended to familiarize the participants with the questions which would be asked as well as the process of estimating the ratio between the two bars.

@@

All responses that incorrectly identified the smaller bar (\(n = 18\)) were removed from the study before analysis; this serves as a basic attention check and leaves 477 valid responses. In addition, one response was removed because the participant did not enter a valid ID for a 3D printed chart.

>>>>

One interesting facet of \citet{clevelandGraphical1984} is the participant recruitment methodology: ``For each experiment the subjects fell into two categories: (1) a group of females, mostly housewives, without substantial technical experience; (2) a mixture of males and females with substantial technical training and working in technical jobs.
Most of the subjects in the position-length experiment participated in the position-angle experiment; in all cases repeat subjects judged the position-angle graphs first.''
It seems likely that the authors recruited individuals within their respective departments as well as their wives.
In order to replicate this atypical participant recruitment method in the modern era, members of the UNL Statistics department and their spouses, partners, and roommates were asked to participate in our study.
This replicates the spirit of the recruitment method without the implicit assumptions that graduate students and professors are male, heterosexual, and have unemployed spouses.
A total of 38 participants completed our study; demographics are shown in \Cref{fig:demographics}.

@@

A Shiny applet was used for data collection, along with the provided kit of 3D printed charts.
Participants provided informed consent through the applet, and then were asked for demographic information (age, gender, education level).
Then, participants were shown a ``practice'' page which allowed them to experiment with the data collection interface and practice estimating the ratio between the bars, as shown in \Cref{fig:practice}. This practice interface did not provide any numeric feedback as to participant correctness, but was merely intended to familiarize the participants with the questions which would be asked as well as the process of estimating the ratio between the two bars.

@@

The participants provided a total of 495 responses.
While each participant was provided with 15 trials, 6 participants partially completed the experiment; one participant did not advance beyond the demographic page.
All responses that incorrectly identified the smaller bar (\(n = 18\)) were removed from the study before analysis; this serves as a basic attention check and leaves 477 valid responses.
In addition, one response was removed because the participant did not enter a valid ID for a 3D printed chart.
